---
title: "FRA Assignment"
author: "Satya"
date: "August 7, 2017"
output: html_document
---

### Load libraries

```{r}

library(DMwR)
library(InformationValue)
library(ROCR)
library(ROSE)
library(party)
library(rpart)
```

### Read Test and Training Data

```{r}
setwd("H:\\GreatLakes\\off campus assignment\\off campus assignment")
traingsrcdata<-read.csv("training.csv")
testingsrcdata<-read.csv("test.csv")

trainingdata<-traingsrcdata
testdata<-testingsrcdata

```

### Clean the data. Out of 5000 records 142 are NA's in training data. so removing NA's
### Out of 1000 records 20 are NA's.in testing data. So removing NA's
```{r}
summary(trainingdata)
summary(testdata)
trainingdata<-na.omit(trainingdata)
testdata<-na.omit(testdata)


```

### Checking the data Issues
```{r}
trainingdata$Casenum<-NULL
testdata$Casenum<-NULL  
  table(trainingdata$SeriousDlqin2yrs)
  table(testdata$SeriousDlqin2yrs)

```

### Un balanced data is observed from above table
### using ROSE we need to do the data balancing for train data
```{r}

trainingdata$SeriousDlqin2yrs<-as.factor(trainingdata$SeriousDlqin2yrs)
testdata$SeriousDlqin2yrs<-as.factor(testdata$SeriousDlqin2yrs)
#trainingDataBalanced<- SMOTE(SeriousDlqin2yrs~.,trainingdata,perc.over = 800)
trainingDataBalanced<- ROSE(SeriousDlqin2yrs~.,trainingdata,seed = 1253)$data

```

### ROSE Data Balance after executing ROSE function

```{r}
table(trainingDataBalanced$SeriousDlqin2yrs)


```

## Logistic regression Modeling
```{r}

logit<- glm(SeriousDlqin2yrs~.,data = trainingDataBalanced,family = binomial)

summary(logit)

```

### Make the preditcitons using predict function

```{r}
    
predictTestDataProbility<-predict(logit,newdata=testdata,type="response")

```

### Build the confusion Matrix
### Compare actual decisions with predictions
```{r}
    
optCutOff <- optimalCutoff(testdata$SeriousDlqin2yrs, predictTestDataProbility)[1] 

confusionMatrix <- confusionMatrix(testdata$SeriousDlqin2yrs,predictTestDataProbility,optCutOff)
confusionMatrix


```

### Miss Classification Error
```{r}
misClassError(testdata$SeriousDlqin2yrs, predictTestDataProbility, threshold = optCutOff)

```

#### Lower the misclassification error, the better is the model

### ROC
```{r}


plotROC(testdata$SeriousDlqin2yrs,predictTestDataProbility)

```

### Decision Trees Modeling
```{r}
library(rattle)				
library(rpart.plot)	
tree <- rpart(SeriousDlqin2yrs~.,method="class", data=trainingDataBalanced)

summary(tree) # detailed summary of splits

title<-"Classification Tree"
  # plot tree 
  rpart.plot(tree, uniform=TRUE,main=title)

```

### Make the preditcitons using predict function

```{r}

predict<-predict(tree,data=testdata)

predict

#table()

```
